1000 Graphs

### 2021-06-24 graphs_newt_snakes/fig_1000.Rmd
I made a graph for how crazy the phenotypes can get under different paramiters. Had fun looping though files. still dont know why some values are in quotes

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0

@@

for (current_file in files){
  print(current_file)

  file <- read.table(current_file, header = TRUE)
  print(max(file$Newt_max_Pheno))
  print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
```

>>>>

I made a mistake. I switched the mutation rates and the effect sizes

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max = 0

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)

  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
  print(newt_max_pheno)
  print(snake_max_pheno)

  if (newt_max_pheno > snake_max_pheno){
    true_max = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max = snake_max_pheno }

```
```{r pressure, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  ylim(0, true_max)+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  theme_bw()

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)

}

p 
```

This is the correct one
```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max_2 = 0

@@

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
  #print(max(file$Newt_max_Pheno))
  #print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)

    if (newt_max_pheno > snake_max_pheno){
    true_max_2 = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max_2 = snake_max_pheno }
```

```{r pressure, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  ylim(0, true_max_2)+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  theme_bw()

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)

}

p 
```
## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked.

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max_3 = 0

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
  #print(max(file$Snake_max_Pheno, na.rm = TRUE))
  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno){
    newt_max_pheno = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }

  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno){
    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)
  if (newt_max_pheno > snake_max_pheno){
    true_max_3 = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max_3 = snake_max_pheno }
```
some of these values are in quotes, why?

```{r pressure, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_3)+
  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
  #scale_y_log10()+
  scale_y_log10(limits=c(0.001,true_max_3))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  theme_bw()

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA

 p <- p +
  geom_line(data=file, aes(y = as.numeric(Newt_mean_Pheno)), color = "darkred",na.rm=TRUE) + 
  geom_line(data=file, aes(y = as.numeric(Snake_mean_Pheno)), color="steelblue", linetype="twodash", na.rm=TRUE) 
  #Sys.sleep(2) na.rm=TRUE

}

p 
```

Some other things that might be goo to look at:
The average of the phenotypes
The difference between the average phenotypes
